Supervised Dimensionality Reduction with Random Projection-Based Ensemble Learning

### 2021-02-17 main.tex
Updates from Overleaf

\subsection{Sparse class boundaries}
We consider the setup
$$X\ | \ Y = 0 \sim N_p(\mathbf{\mu}_0, \Sigma_0) $$
$$X\ | \ Y= 1 \sim N_p(\mathbf{\mu}_1, \Sigma_1) $$
where $\mathbf{\mu}_0 = (1, 0, \dots, 0)$, $\mathbf{\mu}_1 = (-1, 0, \dots, 0)$, $\Sigma_0 = \mathrm{diag}(1, 1, \dots, 1) \ (= I_p)$ and $\Sigma_1 = \mathrm{diag}(1, \lambda, 1, \dots, 1)$. In the simulation shown $\lambda = 0.2$. We see in Figure \ref{fig:simpleboundary} the relatively simple class boundary, mostly dependent upon the value of the first component. We set $p = 100$ so that there are 98 noise components.

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.3in]{figures/simpleboundary.png}
        \caption{The distribution of the two classes in the first two components. All other components are identically distributed between the two classes.\label{fig:simpleboundary}}
    \end{subfigure}%

    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.3in]{figures/simpleeigs.png}
        \caption{The sequence of average projection eigenvalues show a clear distinction for the very first basis vector.}
    \end{subfigure}
    ~ 
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.3in]{figures/simplecomponents.png}
        \caption{Investigating the basis vector corresponding to the distinct eigenvalue shows a strong selection for the first component.}
    \end{subfigure}
\caption{}
\end{figure*}

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.2in]{figures/complexboundary.png}
        \caption{}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.2in]{figures/complexeigs.png}
        \caption{}
    \end{subfigure}

    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.2in]{figures/complexfirst.png}
        \caption{}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[height=2.2in]{figures/complexsecond.png}
        \caption{}
    \end{subfigure}
\caption{}
\end{figure*}

@@

@@

>>>>

\subsection{Sparse class boundaries}

\begin{figure}
    \centering
    \includegraphics[width=5in]{figures/sim1_ev.png}
    \caption{Caption}
    \label{fig:sim1_ev}
\end{figure}

% \begin{figure*}[t!]
%     \centering
%     \begin{subfigure}[t]{0.45\textwidth}
%         \centering
%         \includegraphics[height=2.3in]{figures/simpleboundary.png}
%         \caption{The distribution of the two classes in the first two components. All other components are identically distributed between the two classes.\label{fig:simpleboundary}}
%     \end{subfigure}%

%     \begin{subfigure}[t]{0.45\textwidth}
%         \centering
%         \includegraphics[height=2.3in]{figures/simpleeigs.png}
%         \caption{The sequence of average projection eigenvalues show a clear distinction for the very first basis vector.}
%     \end{subfigure}
%     ~ 
%     \begin{subfigure}[t]{0.45\textwidth}
%         \centering
%         \includegraphics[height=2.3in]{figures/simplecomponents.png}
%         \caption{Investigating the basis vector corresponding to the distinct eigenvalue shows a strong selection for the first component.}
%     \end{subfigure}
% \caption{}
% \end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics{figures/sim2_ev.png}
    \caption{Caption}
    \label{fig:sim2_ev}
\end{figure}

% \begin{figure*}[t!]
%     \centering
%     \begin{subfigure}[t]{0.45\textwidth}
%         \centering
%         \includegraphics[height=2.2in]{figures/complexboundary.png}
%         \caption{}
%     \end{subfigure}%
%     ~
%     \begin{subfigure}[t]{0.45\textwidth}
%         \centering
%         \includegraphics[height=2.2in]{figures/complexeigs.png}
%         \caption{}
%     \end{subfigure}

%     \begin{subfigure}[t]{0.45\textwidth}
%         \centering
%         \includegraphics[height=2.2in]{figures/complexfirst.png}
%         \caption{}
%     \end{subfigure}
%     ~
%     \begin{subfigure}[t]{0.45\textwidth}
%         \centering
%         \includegraphics[height=2.2in]{figures/complexsecond.png}
%         \caption{}
%     \end{subfigure}
% \caption{}
% \end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics{figures/sim3_ev.png}[]
    \caption{Caption}
    \label{fig:sim3_ev}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/sim4_ev.png}
    \caption{Caption}
    \label{fig:sim4_ev}
\end{figure}
